\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex

Power bank sharing is a popular service in Asia, power bank stations are deployed
in markets, stores, and even newsstands. For example, as shown in Figure~\ref{fig:PBS_products},
 there are two power banks station products from China, which are operated by Meituan and Xiaodian respectively. Brick~\cite{Brick} is such a power bank sharing service provider from
  Sweden. It provides power bank rental service all over Sweden and is planning on expanding its
   service around Europe.
\begin{figure}[t]
	\centering
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
	\caption{Two Power Bank Stations.}
	\label{fig:PBS_products}
\end{figure}

>>>>

Power bank sharing is a popular service in Asia, power bank stations are deployed
in markets, stores, and even newsstands. For example, Figure~\ref{fig:PBS_products} are photos
of two power bank stations in China, which are taken outside of a supermarket. Brick~\cite{Brick} is also such a power bank sharing service provider from
Sweden. It provides power bank rental service all over Sweden and is planning on expanding its
service to entire Europe.
\begin{figure}[t]
	\centering
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
	\caption{Two Power Bank Stations.}
	\label{fig:PBS_products}
\end{figure}
